Network Cascades

### 2016-08-26 paper/paper.tex
Reduce magic

Through some generating functions black magic Watts expresses this cascade condition analytically. A cascade is possible if:

@@

\begin{itemize}
  \item $\sum_{k=0}^\infty$: We iterate over all possible thresholds $k$ from $0$ to infinity. The sum converges and in reality it is possible to only calculate the ``first few'' elements
  \item $k (k-1)$ Never mind that. These are remainders of the generating functions black magic.
  \item $\rho_k$ The probability that a node with degree $k$ is vulnerable (according to a probability distribution)
  \item $p_k$ The probability that a node has the threshold $k$ (according to a probability distribution)
  \item $G_0''(1)$ Treat this as an alias for the sum term. It is actually the solution for $x = 1$ of the second derivative of the generating function for the distribution of vulnerable nodes (which is $G_0(x) = \sum_k \rho_kp_kx^k$; the derivative-relationship is clearly visible)
\end{itemize}

>>>>

Through generating functions Watts expresses this cascade condition analytically. A cascade is possible if:

@@

\begin{itemize}
  \item $\sum_{k=0}^\infty$: We iterate over all possible thresholds $k$ from $0$ to infinity. The sum converges and in reality it is possible to only calculate the ``first few'' elements
  \item $k (k-1)$ These are remnants from the generating functions and are not directly relevant to the calculation.
  \item $\rho_k$ The probability that a node with degree $k$ is vulnerable (according to a probability distribution)
  \item $p_k$ The probability that a node has the threshold $k$ (according to a probability distribution)
  \item $G_0''(1)$ Treat this as an alias for the sum term. It is actually the solution for $x = 1$ of the second derivative of the generating function for the distribution of vulnerable nodes (which is $G_0(x) = \sum_k \rho_kp_kx^k$; the derivative-relationship is clearly visible)
\end{itemize}
